---
title: "RWorksheet#5_group.Rmd"
author: "Baylon_Calvario_Calzado"
date: "2024-11-01"
output:
  pdf_document:
   latex_engine: xelatex
  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
4. Select 5 categories from Amazon and select 30 products from each category.
```{r}
library(polite)
library(kableExtra)
library(rmarkdown)
library(httr)
library(rvest)
library(dplyr)
library(stringr)
library(ggplot2)
```

```{r}
urls <- c('https://www.amazon.com/s?k=skin+care&crid=3FODLJK4URUE9&sprefix=skin%2Caps%2C510&ref=nb_sb_ss_ts-doa-p_1_4', 'https://www.amazon.com/s?k=perfume&crid=1MRC8YEDNO62V&sprefix=perfume%2Caps%2C397&ref=nb_sb_noss_1', 'https://www.amazon.com/s?k=bags+for+women&ref=nb_sb_noss', 'https://www.amazon.com/s?k=shoes&crid=QOEP1YQOC5W&sprefix=shoe%2Caps%2C1302&ref=nb_sb_noss_2', 'https://www.amazon.com/s?k=pants&ref=nb_sb_noss')

nameofproduct <- vector("list", length(urls))
price <- vector("list", length(urls))
description <- vector("list", length(urls))
Ratings <- vector("list", length(urls))
Reviews <- vector("list", length(urls))
```


```{r}
df <- list()

for (i in seq_along(urls)) {
    session <- bow(urls[i], user_agent = "Educational")
    webpage <- scrape(session)

nameofproduct[[i]] <-  webpage %>%
  html_nodes('.a-size-base-plus.a-color-base') %>%
  html_text() %>%
  head(30)

price[[i]] <-  webpage %>%
  html_nodes('.a-price-whole') %>%
  html_text() %>%
  head(30)

description[[i]] <-  webpage %>%
  html_nodes('.a-size-mini.a-spacing-none.a-color-base s-line-clamp-3') %>%
  html_text() %>%
  head(30)

Ratings[[i]] <-  webpage %>%
  html_nodes('.a-icon.a-icon-star-small.a-star-small-4-5') %>%
  html_text() %>%
  head(30)

Reviews[[i]] <-  webpage %>%
  html_nodes('.a-size-base-plus.a-color-base') %>%
  html_text() %>%
  head(30)
}
```
5. Extract the price, description, ratings and reviews of each product.

```{r}

skincare <- data.frame(nameofproduct[[1]],
                       Price = price[[1]],
                       Ratings = Ratings[[1]],
                       stringsAsFactors = FALSE
                       )
head(skincare, 50)
skincare %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
```{r}
perfume <- data.frame(nameofproduct[[2]],
                       Price = price[[2]],
                       Ratings = Ratings[[2]],
                       stringsAsFactors = FALSE
                       )
head(perfume, 30)
perfume %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
```{r}
bags <- data.frame(nameofproduct[[3]],
                       Price = price[[3]],
                       Ratings = Ratings[[3]],
                       stringsAsFactors = FALSE
                       )
head(bags, 30)
bags %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
```{r}
shoes <- data.frame(nameofproduct[[4]],
                       Price = price[[4]],
                       Ratings = Ratings[[4]],
                       stringsAsFactors = FALSE
                       )
head(shoes, 30)
shoes %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
```{r}
pants <- data.frame(nameofproduct[[5]],
                       Price = price[[5]],
                       Ratings = Ratings[[5]],
                       stringsAsFactors = FALSE
                       )
head(pants, 30)
pants %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
6. Describe the data you have extracted.

--- Girls please answer this ---

7. What will be your use case for the data you have extracted?

--- Girls please answer this ---

8. Create graphs regarding the use case. And briefly explain it.
```{r}
category_names <- c("Skincare", "Perfume", "Bags", "Shoes", "Pants")
all_data <- bind_rows(
  skincare %>% mutate(Category = "Skincare"),
  perfume %>% mutate(Category = "Perfume"),
  bags %>% mutate(Category = "Bags"),
  shoes %>% mutate(Category = "Shoes"),
  pants %>% mutate(Category = "Pants")
)

all_data$Price <- as.numeric(gsub(",", "", all_data$Price))

ggplot(all_data, aes(x = Category, y = Price)) +
  geom_boxplot(fill = "skyblue") +
  labs(title = "Price Distribution by Product Category", x = "Category", y = "Price") +
  theme_minimal()
```
---Girls explain it---

9. Graph the price and the ratings for each category. Use basic plotting functions and ggplot2
package.
```{r}
ggplot(all_data, aes(x = Price, y = as.numeric(Ratings))) +
  geom_point(aes(color = Category), size = 2) +
  labs(title = "Price vs Ratings by Category", x = "Price", y = "Ratings") +
  theme_minimal() +
  facet_wrap(~ Category, scales = "free")
```

---Girls Explain it---

10. Rank the products of each category by price and ratings. Explain briefly.
```{r}
skincare$Price <- as.numeric(gsub(",", "", skincare$Price))
perfume$Price <- as.numeric(gsub(",", "", perfume$Price))
bags$Price <- as.numeric(gsub(",", "", bags$Price))
shoes$Price <- as.numeric(gsub(",", "", shoes$Price))
pants$Price <- as.numeric(gsub(",", "", pants$Price))

skincare_ranked <- skincare %>% arrange(desc(Price), desc(Ratings))
perfume_ranked <- perfume %>% arrange(desc(Price), desc(Ratings))
bags_ranked <- bags %>% arrange(desc(Price), desc(Ratings))
shoes_ranked <- shoes %>% arrange(desc(Price), desc(Ratings))
pants_ranked <- pants %>% arrange(desc(Price), desc(Ratings))
```


```{r}
head(skincare_ranked, 30)
skincare_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(perfume_ranked, 30)
perfume_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(bags_ranked, 30)
bags_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(shoes_ranked, 30)
shoes_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(pants_ranked, 30)
pants_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
High Price + High Rating: Products ranked at the top of each list with high prices and ratings are generally regarded as premium and popular choices within the category.
Lower Price + High Rating: Products with lower prices but high ratings indicate affordable yet well-received options, highlighting value for money.
#ffdgbfhanafghrjfbrfsjvbmsnfhdjsdg
