---
title: "RWorksheet#5_group.Rmd"
author: "Baylon_Calvario_Calzado"
date: "2024-11-20"
output:
  pdf_document:
   latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(polite)
library(kableExtra)
library(rmarkdown)
library(httr)
library(rvest)
library(dplyr)
library(stringr)
library(ggplot2)
```

```{r}
urls <- c('https://www.amazon.com/s?k=skin+care&crid=3FODLJK4URUE9&sprefix=skin%2Caps%2C510&ref=nb_sb_ss_ts-doa-p_1_4', 'https://www.amazon.com/s?k=perfume&crid=1MRC8YEDNO62V&sprefix=perfume%2Caps%2C397&ref=nb_sb_noss_1', 'https://www.amazon.com/s?k=bags+for+women&ref=nb_sb_noss', 'https://www.amazon.com/s?k=shoes&crid=QOEP1YQOC5W&sprefix=shoe%2Caps%2C1302&ref=nb_sb_noss_2', 'https://www.amazon.com/s?k=pants&ref=nb_sb_noss')

nameofproduct <- vector("list", length(urls))
```


```{r}
df <- list()

for (i in seq_along(urls)) {
    session <- bow(urls[i], user_agent = "Educational")
    webpage <- scrape(session)

nameofproduct[[i]] <-  webpage %>%
  html_nodes('.a-size-base-plus.a-color-base') %>%
  html_text() %>%
  head(10)

}
```
```{r}

skincare <- data.frame(nameofproduct[[1]],
                       stringsAsFactors = FALSE
                       )
head(skincare)
skincare %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

```{r}
perfume <- data.frame(nameofproduct[[2]],
                       Price = price[[2]],
                       Ratings = Ratings[[2]],
                       stringsAsFactors = FALSE
                       )
head(perfume, 30)
perfume %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

```{r}
bags <- data.frame(nameofproduct[[3]],
                       Price = price[[3]],
                       Ratings = Ratings[[3]],
                       stringsAsFactors = FALSE
                       )
head(bags, 30)
bags %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
```{r}
shoes <- data.frame(nameofproduct[[4]],
                       Price = price[[4]],
                       Ratings = Ratings[[4]],
                       stringsAsFactors = FALSE
                       )
head(shoes, 30)
shoes %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

```{r}
pants <- data.frame(nameofproduct[[5]],
                       Price = price[[5]],
                       Ratings = Ratings[[5]],
                       stringsAsFactors = FALSE
                       )
head(pants, 30)
pants %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
6. Describe the data you have extracted.

The extracted dataset contains key details about products across five categories: Skincare, Perfume, Bags, Shoes, and Pants. 
Here's an overview:

Product Name: The titles of the 30 products per category, retrieved from the website.

Price: Numerical values indicating the price, cleaned and standardized for analysis.

Description: Short descriptions highlighting the features of each product.

Ratings: Average star ratings (1 to 5) given by customers, reflecting product quality or satisfaction.

Category: A label indicating which category the product belongs to.

Size: A total of 150 products, with 30 from each category.

The data reveals insights into product characteristics and consumer feedback, aiding in trend analysis and decision-making.

7. What will be your use case for the data you have extracted?

The extracted data can be applied in several practical contexts:

Market Analysis: 
 
 -Identifying price trends and outliers in each category.

 -Analyzing consumer preferences based on product ratings and reviews.


Customer Insights:

-Recommending products with the best quality-price ratio.
Highlighting top-rated or most affordable products in each category.


Retail Strategies:
-Informing inventory stocking by analyzing trends in popular products.

-Pricing strategies for competitive positioning.


Visualization and Reporting:

-Using the data to create visual insights for presentations or reports.

8. Create graphs regarding the use case. And briefly explain it.
```{r}
category_names <- c("Skincare", "Perfume", "Bags", "Shoes", "Pants")
all_data <- bind_rows(
  skincare %>% mutate(Category = "Skincare"),
  perfume %>% mutate(Category = "Perfume"),
  bags %>% mutate(Category = "Bags"),
  shoes %>% mutate(Category = "Shoes"),
  pants %>% mutate(Category = "Pants")
)

all_data$Price <- as.numeric(gsub(",", "", all_data$Price))

ggplot(all_data, aes(x = Category, y = Price)) +
  geom_boxplot(fill = "skyblue") +
  labs(title = "Price Distribution by Product Category", x = "Category", y = "Price") +
  theme_minimal()
```
The boxplot visualizes the distribution of product prices across categories.

Insights:

-The spread of prices varies significantly by category.
-Categories like Bags and Shoes may have higher median prices and broader ranges compared to Skincare or Perfume.


9. Graph the price and the ratings for each category. Use basic plotting functions and ggplot2
package.

```{r}
ggplot(all_data, aes(x = Price, y = as.numeric(Ratings))) +
  geom_point(aes(color = Category), size = 2) +
  labs(title = "Price vs Ratings by Category", x = "Price", y = "Ratings") +
  theme_minimal() +
  facet_wrap(~ Category, scales = "free")
```

The scatter plot illustrates the relationship between price and ratings for each category.

Explanation:

-The relationship is plotted per category using facet_wrap.

-The plot highlights clusters or trends, such as whether higher prices correlate with higher ratings.

-Outliers or inconsistencies in pricing or ratings are easily spotted.

10. Rank the products of each category by price and ratings. Explain briefly.

```{r}
skincare$Price <- as.numeric(gsub(",", "", skincare$Price))
perfume$Price <- as.numeric(gsub(",", "", perfume$Price))
bags$Price <- as.numeric(gsub(",", "", bags$Price))
shoes$Price <- as.numeric(gsub(",", "", shoes$Price))
pants$Price <- as.numeric(gsub(",", "", pants$Price))

skincare_ranked <- skincare %>% arrange(desc(Price), desc(Ratings))
perfume_ranked <- perfume %>% arrange(desc(Price), desc(Ratings))
bags_ranked <- bags %>% arrange(desc(Price), desc(Ratings))
shoes_ranked <- shoes %>% arrange(desc(Price), desc(Ratings))
pants_ranked <- pants %>% arrange(desc(Price), desc(Ratings))
```


```{r}
head(skincare_ranked, 30)
skincare_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(perfume_ranked, 30)
perfume_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(bags_ranked, 30)
bags_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(shoes_ranked, 30)
shoes_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
head(pants_ranked, 30)
pants_ranked %>%
    kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
# High Price + High Rating: Products ranked at the top of each list with high prices and ratings are generally regarded as premium and popular choices within the category.
# Lower Price + High Rating: Products with lower prices but high ratings indicate affordable yet well-received options, highlighting value for money.

# ambot nimo bea
